Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-21 programming23/paper.tex
update daily users + hours for Sep

{Roblox} is a platform for {shared virtual experiences} (typically 3D games), with
65~million Daily Active Users, and 14~billion hours of engagement in
April--June 2023~\cite{corp.roblox.com}.
There are over 5~million distinct user-created programs available on the platform thanks to a
worldwide community of 3~million creators.
Many of the creators program for fun or learning and may
not consider themselves software developers; others are professional
developers.

>>>>

{Roblox} is a platform for {shared virtual experiences} (typically 3D games), with
70~million Daily Active Users, and 16~billion hours of engagement in
July--September 2023~\cite{corp.roblox.com}.
There are over 5~million distinct user-created programs available on the platform thanks to a
worldwide community of 3~million creators.
Many of the creators program for fun or learning and may
not consider themselves software developers; others are professional
developers.
